\documentclass{article}

\usepackage{tabularx}
\usepackage{booktabs}

\renewcommand{\baselinestretch}{1.2}

\title{SE 3XA3: Problem Statement\\ Bomberman 2: Return of the Bomberman}

\author{Team \#18, REM
		\\ Miles Jackson  jacksa7
		\\ Eitan Yehuda  yehudae
		\\ Ridhwan Chowdhury chowdr11
}

\date{}


\begin{document}

%\begin{table}[hp]
%\caption{Revision History} \label{TblRevisionHistory}
%\begin{tabularx}{\textwidth}{llX}
%\toprule
%\textbf{Date} & \textbf{Developer(s)} & \textbf{Change}\\
%\midrule
%Date1 & Name(s) & Description of changes\\
%Date2 & Name(s) & Description of changes\\
%... & ... & ...\\
%\bottomrule
%\end{tabularx}
%\end{table}

\maketitle

Many people especially in current times are stuck at home yet still want to be connected and do things with their friends. Given this, the goal is to create a fun, easy to play game that everyone can enjoy and can be played by multiple players at the same time. The current version of bomberman only supports a single player and has no real objective to win the game. This leaves the game in a state where it is very hard for anyone to enjoy playing it. \\
 
The two main stakeholders of this project are the developers and the players. It is in the developers’ best interest to make a complete version of a product or service given the requirements, time and resources available. In the context of bomberman, it is evident that the current version of the game is novel and needs further development in order to achieve a strong level of engagement. This speaks to the importance for players as stakeholders, as the current iteration of the game does not bring players to play together, nor does it keep them engaged long enough to be entertained with the game. This, in effect, defeats the initial goal of creating a fun game for many to enjoy. \\
 
The game being improved on, is a web-based game which will be available to any personal computer running a Linux based Operating System such as Windows and MacOS. Users will also require an internet connection and access to Google Chrome, Safari, or Microsoft Edge. Due to the controls of the game it will not be available to people accessing those platforms from a mobile environment. \\




\end{document}